\plaintitle

### 2016-05-20 Paper/sp2-paper.tex
Pushed final paper

\documentclass[draft]{sigchi}

@@

Benchmarks are run on both the API server and the database management system.

@@

@@

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{sigchi}
\bibliography{sp2-paper}

>>>>

\documentclass{sigchi}

@@

Benchmarks were ran on both the API server and the database management system.

@@

In Figure 1, it is shown that the database management system, Redis, was able to serve an average of 83,400
requests per second in an Intel Core i7-5600U. It should be noted that Redis is only able to utilize a single core
so scaling through sharding will increase these numbers significantly.

In Figure 2, it can be seen that the requests per second went down
from the database average of 83,400 to 17,600 with low deviation on the same machine.
This shows that the overhead caused by the API server is the bottleneck in this setup. 
Early tests in the API server showed higher number of requests per second
that can be blamed on the addition of URL parsers, data persistence middlewares, and JSON encoders
that likely caused the reduction in the serving-speed. However, these benchmarks only shows its performance
on a dual core system and the API server is highly multithreaded which implies that it could perform much faster
on multicore and multiprocessor servers. Moreover, the API server can also be scaled by using a load balancer
with it running on multiple servers that share the same database.

@@

Based on the results of the system evaluation, we can conclude that the system is efficient enough to handle most 
universities with large student 
populations such as the University of the Philippines Los Baños that has around 13,710 students even if each student
does an API requests once per second. It can be implied that it can also serve populations much larger than the benchmark
results through scaling. 
% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{sigchi}
\bibliography{sp2-paper}
